In this chapter we aim to be as open as possible about the shortcomings of this
thesis. In this way, the reader will be aware that the alteration of these
points may affect the obtained results. The chapter is divided in two parts:
Major and minor, where the major addresses issues which are believed to have
svere impacts on the results, and the minor issues are believed to have a
lesser impact.

\section{Major}
\begin{itemize}[noitemsep,nolistsep]
    \item The plasma is assumed to be isothermal. This assumption would be good
        if the heat flux were enough to equilibriate the temperature
        everywhere in the plasma for the time under consideration.
        However, the heat fluxes are not big enough, and temperature gradients
        has been found experimentally \cite{Schroder2003}.
    \item Not all the boundary conditions are not physically justified. All the
        boundary conditions at the opposite direction of the sheath (given that
        this location is in fact a stagnation point), the sheath boundary
        condition for the velocities $u_{e,\|}$ and $u_{i,\|}$ are somewhat valid
        given that the plasma in the parallel direction are almost in the
        steady state. The numerical boundary condition for $\phi$ at the sheath is valid
        given that the parallel boudary condition for $\Omega^D$ is valid.
        There are however, no reason for why the gradient of $\Omega^D$ should
        be $0$ at the sheath, and it might as well have a fixed gradient.
        Similarily, there is no reason for why the gradient of $n$ should be
        zero at the sheath.
        Perpendicularily we are forcing the system to have zero gradients on
        all fields. As stated before proper treatment of the boundary
        conditions should include the physical behaviour of the surronding
        chasis.
\end{itemize}

FIXME: Move me to BC section
Parallel direction: sheath almost steady state

FIXME: Acutally ok that the collisionality is assumed to be constant as
d/dx nu ei is (under the assumption that Te is constant), 0.5 log(x), which for
high number is almost constant. Just write it in

The collisionality is assumed to be constant. The collisionality will
        vary across the domain. The collisionality is proportional to
        $n\ln(n^{-1/2})=-\frac{1}{2}n\ln(n)$



\section{Minor}

\begin{itemize}[noitemsep,nolistsep]
    \item Treatment of the parallel resistivities. A proper treatmet has
        resulted in oscillations at the edge of the domain which evolves to
        turbulence. The observed turbulence also has a different character as
        there are larger gradients, and more visible structures in the parallel
        direction.
    \item Adding electromagnetic effects. Although this has been reported to
        decrease the run time and increase the stability of the simulations. It
        is here found that the extra terms blows up in $A_\|$.
\end{itemize}
