\chapter*{Acknowledgements}
%
During the work of this thesis I have had the wonderful opportunity to work with, discuss with and obtain help from many people which I would here like to pay my homeage to.

I would like the express my gratitude towards my supervisors Prof. Jens Juul Rasmussen and Prof. Volker Naulin for giving me the opportunity to work in the PPFE group with so brigth and wonderful people.
The many discussion about linear regimes and plasma turbulence with Prof. Rasmussen has been of great help, and his joyful spirit has brigthen my days so many times.
Further, the invaluabl help on the numerical treatment of singularity in the cylinder axis and with the inversion algorithm for the potential from Prof. Naulin is highly appreciated.
So is his grand overview over plasma physics and his remarkable skill to draw fast conclusions from complex physical models

Next, I would like to thank my co-supervisor researcher Jens Madsen for his invaluable insigth in numerics, his patience with my many questions, for helping me with his expertise with curvilinear coordinate systems and for doing everything with a smile on his face.
I have also benefitted greatly from senior scientist Anders Henry Nielsen for his expertise in usage of the super computers.

I have had the pleasure to work with the PPFE's group collaborators at the University of York both during my two study stays, and during the 2014 BOUT++ workshop.
My wholehearted appreciation goes to Dr. Benjamin D. Dudson for his indispensable help, for prioritizing his valuable time to discussions with me and for being so forthcoming.
My thanks also goes to Dr. Jarrod Leddy, Dr. Peter Hill, Dr. David Dickinson and Dr. Brendan Shanahan for the fruitful discussions I have had with them during my stays.
The BOUT++ collaborators also deserves a big thanks for their effort of making BOUT++ a well-tested, documented and easy to use software, and for their technical assistance.

I would like to thank my close colleagues which I have been so lucky to share an office with, namely Ning Yan, Frederik Treue, Asger Schou Jacobsen, Alexander Simon Thrys{\"o}e, Jeppe Miki Busk Olsen, Aslak Sindbjerg Poulsen and Galina Avdeeva. Thank you for the good dicussions and the great humor in the office.
I would especially like to thank Alexander Simon Thrys{\o}e for the lengthful discussion we have had in physics and mathematics, and for the friendship with him and his wife outside the office time.

Besided my colleagues, I have had the most fortunate chance to get to know Dr. Clemens Sch{\"a}fermeier, whom I have spend some great bicycle trips with, and have had many good discussions about philosophy, physics and the Ph.D.-student life with.

My gratitude also goes towards Alexander Simon Thrys{\o}e, Mirko Salewski and Asger Schou Jacobsen for proof-reading this manuscript.

Finally, I would like to thank my family for always supporting me, and I would like to dedicate a very special thanks to my wife, Lenka Magnussen, who has supported me so much during the whole thesis, and for taken so good care of our son during the moments when daddy have had to work late.
I could really not have done this without you!
