\section{Composite derivatives}
\label{sec:compDeriv}
%
In \cref{eq:celma_dens,eq:celma_mom_dens,eq:celma_j_par,eq:celma_vortD_evolution} and \cref{eq:celma_vort_boussinesq} there are some terms which are written as a combination of two or more FD schemes.
These are
%
\begin{align*}
    &\{\phi,\cdot\},&
    &\{\ve{u}_E^2,n\},&
    &\partial_\|\div \L( u_{i,\|}n \frac{\grad_\perp \phi}{B}\R)&
    &\text{and}&
    &\div \L( S_n \L[ \frac{ \grad_\perp \phi }{ B } \R] \R).&
\end{align*}
%
These can either be calculated by applying two (or more) different FD schemes consecutively to a field $f$, or by making a new FD stencil specifically for the operator under consideration.

Special care must be taken at the ghost-points if one chooses to apply two (or more) different FD schemes consecutively.
To see this, we can call $g$ the result of calculating the FD of a field $f$.
As we are using centered stencils (as described in \cref{sec:spat}), then the ghost-points of $g$ is not calculated by the FD%
%
\footnote{There is by definition no way to apply a centered stencil to the last grid point.}%
%
\footnote{One could instead use a one-sided stencil on the ghost-points $f$ when calculating the FD of $f$, so that the ghost-point of $g$ would be known.
This is however not done here.}
%
.

\subsection{Arakawa's stencil}
%
As done in \cref{eq:vecAdvTerm}, we can write $\ve{E}\times\ve{B}$-advective terms (that is the $\{\phi,\cdot\}$ terms) as Poisson brackets.
The proof is found in \cref{app:poisson}.
The benefits of writing terms in Arakawa's form are presented in his paper from 1966 \cite{Arakwa1966}.
In short, the paper shows that a na\"ive FD discretization of the Poisson bracket does not conserve energy and enstrophy.
At the same time it gives an alternative way of discretize in orthogonal curvilinear coordinates in order to keep these quantities conserved.
If the energy and enstrophy are not conserved, fake numerical generation of these quantities occur, which eventually will lead to a blow up of the simulation (in a way described by Phillips in \cite{Phillips1959}).

\subsection{Advection by \texorpdfstring{$\ve{u}_E^2$}{the squared E cross B drift}}
\label{sec:ExBadv}
%
It is also possible to discretize the $\{\ve{u}_E^2, n\}$-term by using Arakawa's method.
We observe that in cylindrical coordinates we have
%
\begin{align*}
    \{\ve{u}_E^2, n\} &= \L\{\L(\frac{\grad_\perp \phi}{B}\R)^2, n\R\}
    \note{Constant $B$}
    \\
    %
    &= \L(\frac{1}{B}\R)^2
    \L\{\L(\L[\ve{e}^{\rho}\partial_{\rho} + \ve{e}^{\theta}\partial_{\theta}\R] \phi\R)
        \cdot
        \L(\L[\ve{e}^{\rho}\partial_{\rho} + \ve{e}^{\theta}\partial_{\theta}\R] \phi\R)
        , n\R\}
    \note{Orthogonality}
    \\
    %
    &= \L(\frac{1}{B}\R)^2
    \L\{g^{\rho\rho}\L(\partial_{\rho} \phi\R)^2+
        g^{\theta\theta}\L(\partial_{\theta} \phi\R)^2
        , n\R\}
    \\
    %
    &= \L(\frac{1}{B}\R)^2
    \L\{\L(\partial_{\rho} \phi\R)^2+ \frac{1}{\rho^2}\L(\partial_{\theta} \phi\R)^2
        , n\R\}.
        \numberthis
        \label{eq:ExBAdvImp}
\end{align*}
%
Here, care must be taken when treating the ghost-points.
No ghost-points are needed in the $\theta$ direction, as this is periodic.
Thus, for $\partial_{\theta} \phi$ we only need to make sure that we take the $\theta$ derivatives at the ghost-points in $\rho$.

For $\partial_{\rho} \phi$, we must re-apply the values in the $\rho$ ghost-points as the derivative is not calculated there.
For the inner ghost-point, the same procedure as used in \cref{sec:ghostRhoDeriv} can be used.
For the outer ghost-point, we can use \cref{eq:extraPolUp} for extrapolation to the ghost-point.

This way of discretizing is second order accurate, as indicated in \cref{tb:MESResults}.


\subsection{\texorpdfstring{$\div(g\grad_\perp f)$}{Divergence of g times the perpendicular gradient of f} terms}
%
We have that
%
\begin{align*}
    \div(f\nabla_\perp g)
    =& f\grad_\perp^2g + \grad f\cdot       \grad_\perp g
    \\
    =& f\grad_\perp^2g + \grad_\perp f\cdot \grad_\perp g
    \note{See \cref{sec:perpLapl}}
    \\
    =&
    f\L(g^{ij} \partial_i \partial_j + G^j \partial_j -\frac{1}{J} \partial_z \L(\frac{J}{g_{zz}} \partial_2\R)\R)g
    +
    \L(e^\rho \partial_\rho  + e^\theta \partial_\theta \R)f\cdot \L(e^\rho \partial_\rho  + e^\theta \partial_\theta \R)g
    \\
    =&
    f\L(g^{ij} \partial_i \partial_j + G^j \partial_j -\frac{1}{J} \partial_z \L(\frac{J}{g_{zz}} \partial_2\R)\R)g
    +
    g^{\rho\rho} \partial_\rho f \partial_\rho g
    +
    g^{\rho\theta} \partial_\rho f  \partial_\theta g
    +
    g^{\theta\rho} \partial_\theta f  \partial_\rho g
    +
    g^{\theta\theta} \partial_\theta f \partial_\theta g.
    \numberthis
    \label{eq:perpPerpDeriv}
\end{align*}
%
As BOUT++ includes a numerical operator for $\grad_\perp^2g$ (as mentioned in \cref{sec:perpLapl}), we could have used this operator for calculating $f\grad_\perp^2g$.
However, from \cref{app:coord}, we get that
%
\begin{align*}
  G^\rho =& \frac{1}{J}\\
  G^z =& 0\\
  G^\theta =& 0\\
  g^{ij} =& 0 \qquad i\neq j\\
  g^{\rho\rho} =& 1\\
  g^{\theta\theta} =& \frac{1}{\rho^2}\\
  g^{zz}\partial_z^2 - \frac{1}{J}\partial_z\left(\frac{J}{g^{zz}}\partial_z\right) =& 0,
\end{align*}
%
for cylindrical coordinates.
Thus, \cref{eq:perpPerpDeriv} can be rewritten to
%
\begin{align*}
    &f\L(g^{\rho\rho} \partial_\rho \partial_\rho + g^{\theta\theta} \partial_\theta \partial_\theta + G^\rho \partial_\rho \R)g
    + g^{\rho\rho} \partial_\rho f \partial_\rho g
    + g^{\theta\theta} \partial_\theta f \partial_\theta g
    \\
    =&
    f \partial^2_\rho g
    + f \frac{1}{\rho^2}\partial^2_\theta g
    + f\frac{1}{\rho}\partial_\rho g
    +  \partial_\rho f \partial_\rho g
    +  \frac{1}{\rho^2} \partial_\theta f \partial_\theta g,
    \numberthis
    \label{eq:ownPerp}
\end{align*}
%
Calculation of \cref{eq:ownPerp} requires less arithmetic operations than \cref{eq:perpPerpDeriv}, and is therefore used in the CELMA code.

\subsection{Parallel derivative of the divergence of the cross term}
%
As $\partial_\|\div \L( u_{i,\|}n \frac{\grad_\perp \phi}{B}\R)$ can be rewritten to $\partial_\|\div(g\grad_\perp f)$, we just have to take care of the parallel ghost-points of $\div \L( u_{i,\|}n \frac{\grad_\perp \phi}{B}\R)$ before taking the parallel derivative.
We can use \cref{eq:extraPolUp} for calculation of the upper ghost-point, and \cref{eq:extraPolDown}  for calculation of the lower ghost-point.
